### 2022-09-21 main/chapter_context.tex
write some on inner tracker

Our search paper~\cite{atlas2022searches} contains concise and standard
descriptions of the \atlas\ detector and its relevant components.
Through its many inexact reproductions in past \atlas\ publications, the text
of these descriptions has become so highly refined that my attempts to improve
upon it would be in vain.
Instead, this section quotes our published text with explanatory commentary.

\begin{quote}
``%
The ATLAS detector~\cite{PERF-2007-01} is a multipurpose particle detector with
a forward--backward symmetric cylindrical geometry and a near $4\pi$ coverage
in solid angle.%
\footnote{%
``ATLAS uses a right-handed coordinate system with its origin at the nominal
interaction point (IP) in the centre of the detector and the $z$-axis along the
beam pipe.
The $x$-axis points from the IP to the centre of the LHC ring, and the $y$-axis
points upwards.
Cylindrical coordinates $(r,\phi)$ are used in the transverse plane, $\phi$
being the azimuthal angle around the $z$-axis.
The pseudorapidity is defined in terms of the polar angle $\theta$ as
$\eta = -\ln \tan(\theta/2)$.
Angular distance is measured in units of
$\Delta R \equiv \sqrt{(\Delta\eta)^{2} + (\Delta\phi)^{2}}$.%
''\footnotemark~\cite{atlas2022searches}%
}
It consists of an inner tracking detector surrounded by a thin superconducting
solenoid providing a $2\,\mathrm{T}$ axial magnetic field, electromagnetic and
hadronic calorimeters, and a muon spectrometer.%
''~\cite{atlas2022searches}
\end{quote}
To illustrate this description, a vertical slice of \atlas\ is displayed in
Figure~\ref{fig:atlas_cutaway}, and each subsystem is described in more detail
in a subsection below:
the inner detector in Section~\ref{sec:atlas_inner},
the electromagnetic and hadronic calorimeter systems in
Section~\ref{sec:atlas_calo},
and
the chambers of the muon spectrometer in Section~\ref{sec:atlas_muon}.
The final connection to the data analysed in this thesis is made through the
trigger system which is described in Section~\ref{sec:atlas_trigger},
and details of the data themselves are given in
Section~\ref{sec:atlas_data}

\footnotetext{%
This footnote, which was perfected in~\cite{lester2013heffalon},
``should be used in every \atlas\ publication''~\cite{atlas_footnote}.
True to form, internal \atlas\ guidelines ask that
``If you think you can improve on it, please consult with the
Publications Committee''~\cite{atlas_coordinate}.
We somehow added the sentence defining angular distance without such a
consultation.%
}

@@

\subsection{Inner detector}
\label{sec:atlas_inner}
\TODO{inner detector}
\begin{quote}
``%
The inner tracking detector covers the pseudorapidity range $|\eta| < 2.5$.
It consists of silicon pixel, silicon microstrip, and transition radiation
tracking detectors.
An additional layer of silicon pixels, the insertable
B-layer~\cite{ATLAS-TDR-19, PIX-2018-001}, was installed before Run~2.%
''~\cite{atlas2022searches}
\end{quote}

\TODO{upgraded with IBL}

\subsection{Calorimeters}
\label{sec:atlas_calo}
\TODO{calo}
\begin{quote}
``%
Lead/liquid-argon (LAr) sampling calorimeters provide electromagnetic (EM)
energy measurements with high granularity.
A steel/scintillator-tile hadron calorimeter covers the central pseudorapidity
range ($|\eta| < 1.7$).
The endcap and forward regions are instrumented with LAr calorimeters for both
the EM and hadronic energy measurements up to $|\eta| = 4.9$.%
''~\cite{atlas2022searches}
\end{quote}

The `A' in \atlas\ does not stand for Argon, but perhaps it should.

>>>>

Our search paper~\cite{atlas2022searches} contains concise and standard
descriptions of the \atlas\ detector and its relevant components.
Through its many inexact reproductions in past \atlas\ publications, the text
of these descriptions has become so highly refined that attempts to improve
it myself would probably be in vain.
Instead, this section quotes our published text with explanatory commentary.

@@

\begin{quote}
``%
The ATLAS detector~\cite{PERF-2007-01} is a multipurpose particle detector with
a forward--backward symmetric cylindrical geometry and a near $4\pi$ coverage
in solid angle.%
\footnote{%
``ATLAS uses a right-handed coordinate system with its origin at the nominal
interaction point (IP) in the centre of the detector and the $z$-axis along the
beam pipe.
The $x$-axis points from the IP to the centre of the LHC ring, and the $y$-axis
points upwards.
Cylindrical coordinates $(r,\phi)$ are used in the transverse plane, $\phi$
being the azimuthal angle around the $z$-axis.
The pseudorapidity is defined in terms of the polar angle $\theta$ as
$\eta = -\ln \tan(\theta/2)$.
Angular distance is measured in units of
$\Delta R \equiv \sqrt{(\Delta\eta)^{2} + (\Delta\phi)^{2}}$.%
''\footnotemark~\cite{atlas2022searches}%
}
It consists of an inner tracking detector surrounded by a thin superconducting
solenoid providing a $2\,\mathrm{T}$ axial magnetic field, electromagnetic and
hadronic calorimeters, and a muon spectrometer.%
''~\cite{atlas2022searches}
\end{quote}
To illustrate this description, a vertical slice of \atlas\ is displayed in
Figure~\ref{fig:atlas_cutaway}, and each subsystem is described in more detail
in a subsection below:
the inner tracking detector in Section~\ref{sec:atlas_inner},
the electromagnetic and hadronic calorimeter systems in
Section~\ref{sec:atlas_calo},
and
the chambers of the muon spectrometer in Section~\ref{sec:atlas_muon}.
The final connection to the data analysed in this thesis is made through the
trigger system which is described in Section~\ref{sec:atlas_trigger},
and details of the data themselves are given in
Section~\ref{sec:atlas_data}

\footnotetext{%
This footnote, which was perfected in~\cite{lester2013heffalon},
``should be used in every \atlas\ publication''~\cite{atlas_footnote}.
True to form, internal \atlas\ guidelines ask that
``If you think you can improve on it, please consult with the
Publications Committee''~\cite{atlas_coordinate}.
We added the sentence defining angular distance without such a consultation.%
}

\subsection{Inner detector}
\label{sec:atlas_inner}
The inner tracking detectors begin \atlas' measurements of new collisions
by precisely tracing the paths taken by energetic charged particles
as they curve through the solenoidal magnetic field.
Track curvature provides momentum information,
tracks' associations into collision vertices helps to separate
pile-up,
and their associations into displaced vertices help to identify
particle decays.

Our description continues:
\begin{quote}
``%
The inner tracking detector covers the pseudorapidity range $|\eta| < 2.5$.
It consists of silicon pixel, silicon microstrip, and transition radiation
tracking detectors.
An additional layer of silicon pixels, the insertable
B-layer~\cite{ATLAS-TDR-19, PIX-2018-001}, was installed before Run~2.%
''~\cite{atlas2022searches}
\end{quote}
The insertable B-layer is a silicon pixel detector that begins just
$3\,\textrm{cm}$ from the beam-pipe, and provides robust tracking for the
present and future high LHC luminosities,
particularly for sensitivity to `Goldilocks Zone' particles
(B-hadrons, occasionally tau leptons, and maybe new species) whose expected
lifetimes are just right to decay inside the tracking system.
Following radially outwards, the silicon pixel and silicon microstrip%
\footnote{%
Formerly known as the SemiConductor Tracker~\cite{atlas1999design1},
the silicon microstrip system retains the
SCT~\cite{atlas2008experiment}.%
}
detectors (which use silicon technology)
and the transition radiation tracking detectors (which uses straw tubes).

As for the whole \atlas\ detector, complete $\phi$ coverage and a large $\eta$
range minimizes leakage.
Towards \atlas' design goals, this inner tracking detector crucially provides
measurements of electrons, B-hadrons, and the missing transverse momentum.

\subsection{Calorimeters}
\label{sec:atlas_calo}
The `A' in \atlas\ does not stand for Argon, but perhaps it should.
\TODO{calo}
\begin{quote}
``%
Lead/liquid-argon (LAr) sampling calorimeters provide electromagnetic (EM)
energy measurements with high granularity.
A steel/scintillator-tile hadron calorimeter covers the central pseudorapidity
range ($|\eta| < 1.7$).
The endcap and forward regions are instrumented with LAr calorimeters for both
the EM and hadronic energy measurements up to $|\eta| = 4.9$.%
''~\cite{atlas2022searches}
\end{quote}
